Inference methods comparison for the simplified Naomi model

### 2023-04-20 src/naomi-simple_compare/comparison.Rmd
Update naomi-simple_compare and run through

<!-- ## `beta_alpha` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_helper("beta_alpha") -->
<!-- ``` -->

<!-- ## `beta_lambda` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_helper("beta_lambda") -->
<!-- ``` -->

<!-- ## `beta_anc_rho` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf("beta_anc_rho") -->
<!-- ``` -->

<!-- ## `beta_anc_alpha` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf("beta_anc_alpha") -->
<!-- ``` -->

<!-- ## `logit` -->

<!-- ```{r eval = FALSE} -->
<!-- lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf) -->
<!-- ``` -->

<!-- ## `log_sigma` -->

<!-- ```{r eval = FALSE} -->
<!-- lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf) -->
<!-- ``` -->

<!-- ## `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_x") -->
<!-- ``` -->

<!-- ## `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_x") -->
<!-- ``` -->

<!-- ## `us_rho_x` -->

<!-- ```{r eval = pars_eval[["us_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("us_rho_x") -->
<!-- ``` -->

<!-- ## `u_rho_xs` -->

<!-- ```{r eval = pars_eval[["u_rho_xs"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_xs") -->
<!-- ``` -->

<!-- ## `us_rho_xs` -->

<!-- ```{r eval = pars_eval[["us_rho_xs"]]} -->
<!-- histogram_and_ecdf_helper("us_rho_xs") -->
<!-- ``` -->

<!-- ## `u_rho_as` -->

<!-- ```{r eval = pars_eval[["u_rho_as"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_as") -->
<!-- ``` -->

<!-- ## `u_alpha_x` -->

<!-- ```{r eval = pars_eval[["u_alpha_x"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_x") -->
<!-- ``` -->

<!-- ## `us_alpha_x` -->

<!-- ```{r eval = pars_eval[["us_alpha_x"]]} -->
<!-- histogram_and_ecdf_helper("us_alpha_x") -->
<!-- ``` -->

<!-- ## `u_alpha_xs` -->

<!-- ```{r eval = pars_eval[["u_alpha_xs"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_xs") -->
<!-- ``` -->

<!-- ## `us_alpha_xs` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_helper("us_alpha_xs") -->
<!-- ``` -->

<!-- ## `u_alpha_a` -->

<!-- ```{r eval = pars_eval[["u_alpha_a"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_a") -->
<!-- ``` -->

<!-- ## `u_alpha_as` -->

<!-- ```{r eval = pars_eval[["u_alpha_as"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_as") -->
<!-- ``` -->

<!-- ## `u_alpha_xa` -->

<!-- ```{r eval = pars_eval[["u_alpha_xa"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_xa") -->
<!-- ``` -->

<!-- ## `ui_lambda_x` -->

<!-- ```{r eval = pars_eval[["ui_lambda_x"]]} -->
<!-- histogram_and_ecdf_helper("ui_lambda_x") -->
<!-- ``` -->

<!-- ## `ui_anc_rho_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("ui_anc_rho_x") -->
<!-- ``` -->

<!-- ## `ui_anc_alpha_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_alpha_x"]]} -->
<!-- histogram_and_ecdf_helper("ui_anc_alpha_x") -->
<!-- ``` -->

<!-- ## `log_or_gamma` -->

<!-- ```{r eval = pars_eval[["log_or_gamma"]]} -->
<!-- histogram_and_ecdf_helper("log_or_gamma") -->
<!-- ``` -->

@@

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% unique(names(tmb$fit$obj$env$par)))]
```
The most important ones (checked with Jeff) are HIV prevalence (`rho_t1_out`), ART coverage (`alpha_t1_out`), and HIV incidence (`lambda_t1_out`).

@@

```{r}
ks_helper("beta", starts_with = TRUE)
ks_helper("beta", starts_with = TRUE, method1 = "TMB", method2 = "adam")
```

<!-- ### `logit` -->

<!-- ```{r} -->
<!-- ks_helper("logit", starts_with = TRUE) -->
<!-- ks_helper("logit", starts_with = TRUE, method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `log_sigma` -->

<!-- ```{r} -->
<!-- ks_helper("log_sigma", starts_with = TRUE) -->
<!-- ks_helper("log_sigma", starts_with = TRUE , method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- ks_helper("u_rho_x") -->
<!-- ks_helper("u_rho_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_xs` -->

<!-- ```{r eval = pars_eval[["u_rho_xs"]]} -->
<!-- ks_helper("u_rho_xs") -->
<!-- ks_helper("u_rho_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_rho_x` -->

<!-- ```{r eval = pars_eval[["us_rho_x"]]} -->
<!-- ks_helper("us_rho_x") -->
<!-- ks_helper("us_rho_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_rho_xs` -->

<!-- ```{r eval = pars_eval[["us_rho_xs"]]} -->
<!-- ks_helper("us_rho_xs") -->
<!-- ks_helper("us_rho_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_a` -->

<!-- ```{r eval = pars_eval[["u_rho_a"]]} -->
<!-- ks_helper("u_rho_a") -->
<!-- ks_helper("u_rho_a", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_as` -->

<!-- ```{r eval = pars_eval[["u_rho_as"]]} -->
<!-- ks_helper("u_rho_as") -->
<!-- ks_helper("u_rho_as", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_x` -->

<!-- ```{r eval = pars_eval[["u_alpha_x"]]} -->
<!-- ks_helper("u_alpha_x") -->
<!-- ks_helper("u_alpha_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_xs` -->

<!-- ```{r eval = pars_eval[["u_alpha_xs"]]} -->
<!-- ks_helper("u_alpha_xs") -->
<!-- ks_helper("u_alpha_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_alpha_x` -->

<!-- ```{r eval = pars_eval[["us_alpha_x"]]} -->
<!-- ks_helper("us_alpha_x") -->
<!-- ks_helper("us_alpha_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_alpha_xs` -->

<!-- ```{r eval = pars_eval[["us_alpha_xs"]]} -->
<!-- ks_helper("us_alpha_xs") -->
<!-- ks_helper("us_alpha_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_a` -->

<!-- ```{r eval = pars_eval[["u_alpha_a"]]} -->
<!-- ks_helper("u_alpha_a") -->
<!-- ks_helper("u_alpha_a", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_as` -->

<!-- ```{r eval = pars_eval[["u_alpha_as"]]} -->
<!-- ks_helper("u_alpha_as") -->
<!-- ks_helper("u_alpha_as", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_xa` -->

<!-- ```{r eval = pars_eval[["u_alpha_xa"]]} -->
<!-- ks_helper("u_alpha_xa") -->
<!-- ks_helper("u_alpha_xa", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `ui_anc_rho_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_rho_x"]]} -->
<!-- ks_helper("ui_anc_rho_x") -->
<!-- ks_helper("ui_anc_rho_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `ui_anc_alpha_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_alpha_x"]]} -->
<!-- ks_helper("ui_anc_alpha_x") -->
<!-- ks_helper("ui_anc_alpha_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `log_or_gamma` -->

<!-- ```{r eval = pars_eval[["log_or_gamma"]]} -->
<!-- ks_helper("log_or_gamma") -->
<!-- ks_helper("log_or_gamma", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

@@

```{r}
ks_rho_t1_out <- to_ks_df(par = "rho_t1_out", outputs = TRUE, id = mf_out_fine$id)

merge_to_mf_out_fine <- function(ks_df) {
  ks_df %>%
  select(-par) %>%
  left_join(
    mf_out_fine %>%
      rename("full_id" = "id") %>%
      tibble::rowid_to_column("index") %>%
      mutate(index = as.numeric(index))
  ) %>%
  select(-index)
}

ks_rho_t1_out <- merge_to_mf_out_fine(ks_rho_t1_out)

ks_alpha_t1_out <- to_ks_df(par = "alpha_t1_out", outputs = TRUE, id = mf_out_fine$id) %>%
  merge_to_mf_out_fine()

ks_lambda_t1_out <- to_ks_df(par = "lambda_t1_out", outputs = TRUE, id = mf_out_fine$id) %>%
  merge_to_mf_out_fine()

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out")
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out")
ks_plot(ks_df = ks_lambda_t1_out, par = "lambda_t1_out")
```

@@

```{r}
options(dplyr.summarise.inform = FALSE)

@@

ks_summary <- ks_summary %>%
  left_join(dict, by = "Parameter")
```

Values in green are the lowest KS difference for that particular parameter:

```{r}
ks_summary %>%
  gt::gt() %>%
  gt::fmt_number(
    columns = starts_with("KS"),
    decimals = 3
  ) %>%
  gt::tab_style(
    style = cell_fill(color = "#009E73"),
    locations = cells_body(
      columns = `KS(adam, tmbstan)`,
      rows = `KS(adam, tmbstan)` < `KS(aghq, tmbstan)` & `KS(adam, tmbstan)` < `KS(TMB, tmbstan)`
    )
  ) %>%
    gt::tab_style(
    style = cell_fill(color = "#009E73"),
    locations = cells_body(
      columns = `KS(aghq, tmbstan)`,
      rows = `KS(aghq, tmbstan)` < `KS(adam, tmbstan)` & `KS(aghq, tmbstan)` < `KS(TMB, tmbstan)`
    )
  ) %>%
    gt::tab_style(
    style = cell_fill(color = "#009E73"),
    locations = cells_body(
      columns = `KS(TMB, tmbstan)`,
      rows = `KS(TMB, tmbstan)` < `KS(aghq, tmbstan)` & `KS(TMB, tmbstan)` < `KS(adam, tmbstan)`
    )
  )
```

This plot could be improved by making the red to green transition smooth, then adding legend for KS difference.
The density plots could be filled according to KS difference.

```{r}
summary_ks_plot <- function(ks_summary, method1, method2) {
  ks_method1 <- paste0("KS(", method1, ", tmbstan)")
  ks_method2 <- paste0("KS(", method2, ", tmbstan)")

  xy_length <- min(1, max(ks_summary[[ks_method1]], ks_summary[[ks_method2]]) + 0.05)

  x <- y <- seq(0, xy_length, length.out = 20)

  gradient_base <- expand.grid(x, y) %>%
    mutate(diff = Var1 - Var2) %>%
    ggplot(aes(x = Var1, y = Var2)) +
    geom_tile(aes(fill = diff), alpha = 0.7) +
    scale_fill_gradientn(
      colours = c("#56B4E9", "white", "#009E73"),
      rescaler = ~ scales::rescale_mid(.x, mid = 0)
    )

  densityplot <- gradient_base +
    stat_density_2d(data = ks_summary, aes(x = .data[[ks_method1]], y = .data[[ks_method2]], linetype = Type), col = "black") +
    xlim(0, xy_length) +
    ylim(0, xy_length) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
    scale_linetype_manual(values = c("solid", "dashed")) +
    labs(x = ks_method1, y = ks_method2) +
    theme_minimal() +
    guides(fill = "none") +
    theme(
      legend.position = "bottom"
    )

  ks_summary[["KS difference"]] <- ks_summary[[ks_method1]] - ks_summary[[ks_method2]]

  ridgeplot <- ggplot(ks_summary, aes(y = Type, x = `KS difference`)) +
    ggridges::geom_density_ridges(alpha = 0.7, fill = NA, aes(linetype = Type)) +
    coord_flip() +
    scale_linetype_manual(values = c("solid", "dashed")) +
    labs(y = "", x = paste0(ks_method1, " - ", ks_method2)) +
    guides(linetype = FALSE) +
    theme_minimal()

  densityplot + ridgeplot
}

ks_summary %>%
  filter(Type != "Hyper") %>%
  summary_ks_plot("TMB", "aghq")

summary_ks_plot(ks_summary, "TMB", "aghq")
summary_ks_plot(ks_summary, "TMB", "adam")
summary_ks_plot(ks_summary, "aghq", "adam")

(ks_summary_out <- ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  ))
```
Compute $p$-values, then plot expecting $\mathcal{U}(0, 1)$.
If not conclude there is a significant difference.

@@

```{r}
pdf("ks_summary_tmb_adam.pdf", h = 4, w = 6.25)
summary_ks_plot(ks_summary, "TMB", "adam")
dev.off()

saveRDS(ks_summary_out, "ks_summary_out.rds")
```

>>>>

## `beta_alpha`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_alpha")
```

## `beta_lambda`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_lambda")
```

## `beta_anc_rho`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf("beta_anc_rho")
```

## `beta_anc_alpha`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf("beta_anc_alpha")
```

## `logit`

```{r eval = FALSE}
lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf)
```

## `log_sigma`

```{r eval = FALSE}
lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf)
```

## `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
histogram_and_ecdf_helper("u_rho_x")
```

## `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
histogram_and_ecdf_helper("u_rho_x")
```

## `us_rho_x`

```{r eval = pars_eval[["us_rho_x"]]}
histogram_and_ecdf_helper("us_rho_x")
```

## `u_rho_xs`

```{r eval = pars_eval[["u_rho_xs"]]}
histogram_and_ecdf_helper("u_rho_xs")
```

## `us_rho_xs`

```{r eval = pars_eval[["us_rho_xs"]]}
histogram_and_ecdf_helper("us_rho_xs")
```

## `u_rho_as`

```{r eval = pars_eval[["u_rho_as"]]}
histogram_and_ecdf_helper("u_rho_as")
```

## `u_alpha_x`

```{r eval = pars_eval[["u_alpha_x"]]}
histogram_and_ecdf_helper("u_alpha_x")
```

## `us_alpha_x`

```{r eval = pars_eval[["us_alpha_x"]]}
histogram_and_ecdf_helper("us_alpha_x")
```

## `u_alpha_xs`

```{r eval = pars_eval[["u_alpha_xs"]]}
histogram_and_ecdf_helper("u_alpha_xs")
```

## `us_alpha_xs`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("us_alpha_xs")
```

## `u_alpha_a`

```{r eval = pars_eval[["u_alpha_a"]]}
histogram_and_ecdf_helper("u_alpha_a")
```

## `u_alpha_as`

```{r eval = pars_eval[["u_alpha_as"]]}
histogram_and_ecdf_helper("u_alpha_as")
```

## `u_alpha_xa`

```{r eval = pars_eval[["u_alpha_xa"]]}
histogram_and_ecdf_helper("u_alpha_xa")
```

## `ui_lambda_x`

```{r eval = pars_eval[["ui_lambda_x"]]}
histogram_and_ecdf_helper("ui_lambda_x")
```

## `ui_anc_rho_x`

```{r eval = pars_eval[["ui_anc_rho_x"]]}
histogram_and_ecdf_helper("ui_anc_rho_x")
```

## `ui_anc_alpha_x`

```{r eval = pars_eval[["ui_anc_alpha_x"]]}
histogram_and_ecdf_helper("ui_anc_alpha_x")
```

## `log_or_gamma`

```{r eval = pars_eval[["log_or_gamma"]]}
histogram_and_ecdf_helper("log_or_gamma")
```

@@

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% unique(names(tmb$fit$obj$env$par)))]
```
The most important ones (this has been checked with Jeff) are HIV prevalence (`rho_t1_out`), ART coverage (`alpha_t1_out`), and HIV incidence (`lambda_t1_out`).

@@

```{r}
ks_helper("beta", starts_with = TRUE)
```

### `logit`

```{r}
ks_helper("logit", starts_with = TRUE)
```

### `log_sigma`

```{r}
ks_helper("log_sigma", starts_with = TRUE)
```

### `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
ks_helper("u_rho_x")
```

### `u_rho_xs`

```{r eval = pars_eval[["u_rho_xs"]]}
ks_helper("u_rho_xs")
```

### `us_rho_x`

```{r eval = pars_eval[["us_rho_x"]]}
ks_helper("us_rho_x")
```

### `us_rho_xs`

```{r eval = pars_eval[["us_rho_xs"]]}
ks_helper("us_rho_xs")
```

### `u_rho_a`

```{r eval = pars_eval[["u_rho_a"]]}
ks_helper("u_rho_a")
```

### `u_rho_as`

```{r eval = pars_eval[["u_rho_as"]]}
ks_helper("u_rho_as")
```

### `u_alpha_x`

```{r eval = pars_eval[["u_alpha_x"]]}
ks_helper("u_alpha_x")
```

### `u_alpha_xs`

```{r eval = pars_eval[["u_alpha_xs"]]}
ks_helper("u_alpha_xs")
```

### `us_alpha_x`

```{r eval = pars_eval[["us_alpha_x"]]}
ks_helper("us_alpha_x")
```

### `us_alpha_xs`

```{r eval = pars_eval[["us_alpha_xs"]]}
ks_helper("us_alpha_xs")
```

### `u_alpha_a`

```{r eval = pars_eval[["u_alpha_a"]]}
ks_helper("u_alpha_a")
```

### `u_alpha_as`

```{r eval = pars_eval[["u_alpha_as"]]}
ks_helper("u_alpha_as")
```

### `u_alpha_xa`

```{r eval = pars_eval[["u_alpha_xa"]]}
ks_helper("u_alpha_xa")
```

### `ui_anc_rho_x`

```{r eval = pars_eval[["ui_anc_rho_x"]]}
ks_helper("ui_anc_rho_x")
```

### `ui_anc_alpha_x`

```{r eval = pars_eval[["ui_anc_alpha_x"]]}
ks_helper("ui_anc_alpha_x")
```

### `log_or_gamma`

```{r eval = pars_eval[["log_or_gamma"]]}
ks_helper("log_or_gamma")
```

@@

```{r}
ks_df_out <- function(par) {
  to_ks_df(par = par, outputs = TRUE, id = mf_out_fine$id) %>%
  select(-par) %>%
  left_join(
    mf_out_fine %>%
      rename("full_id" = "id") %>%
      tibble::rowid_to_column("index") %>%
      mutate(index = as.numeric(index))
  )
}

ks_rho_t1_out <- ks_df_out(par = "rho_t1_out")
ks_alpha_t1_out <- ks_df_out(par = "alpha_t1_out")
ks_lambda_t1_out <- ks_df_out(par = "lambda_t1_out")

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_lambda_t1_out, par = "lambda_t1_out", alpha = 0.2)
```

@@

Values in dark blue are the lowest KS difference for that particular parameter:

```{r class.source = 'fold-hide'}
options(dplyr.summarise.inform = FALSE)

@@

ks_summary <- ks_summary %>%
  left_join(dict, by = "Parameter")

ks_summary %>%
  gt::gt() %>%
  gt::fmt_number(
    columns = starts_with("KS"),
    decimals = 3
  ) %>%
  gt::tab_style(
    style = cell_fill(color = "#0072B2"),
    locations = cells_body(
      columns = `KS(adam, tmbstan)`,
      rows = `KS(adam, tmbstan)` < `KS(aghq, tmbstan)` & `KS(adam, tmbstan)` < `KS(TMB, tmbstan)`
    )
  ) %>%
    gt::tab_style(
    style = cell_fill(color = "#0072B2"),
    locations = cells_body(
      columns = `KS(aghq, tmbstan)`,
      rows = `KS(aghq, tmbstan)` < `KS(adam, tmbstan)` & `KS(aghq, tmbstan)` < `KS(TMB, tmbstan)`
    )
  ) %>%
    gt::tab_style(
    style = cell_fill(color = "#0072B2"),
    locations = cells_body(
      columns = `KS(TMB, tmbstan)`,
      rows = `KS(TMB, tmbstan)` < `KS(aghq, tmbstan)` & `KS(TMB, tmbstan)` < `KS(adam, tmbstan)`
    )
  )
```

```{r}
ks_summary %>%
  filter(Type != "Hyper") %>%
  ks_plot_many("TMB", "aghq")

(ks_summary_out <- ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  )) %>%
  gt::gt()
```

@@

```{r}
saveRDS(ks_summary_out, "ks_summary_out.rds")
```
